Pillar 2 - (STM) Topic Modeling

### 2019-03-28 Pillar 2 -(STM) Topic Modeling.Rmd
Template for (STM) Topic Model, runs until evaluation

---
title: "Pillar 2 - Topic Modeling"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
---

@@

library(ggwordcloud) # Word Clouds
library(topicmodels)
library(lemon)
library(ggthemes)
library(rlang) #quote
library(ldatuning) # ideal number of topics in LDA

@@

# LDA
##Setup
###Cast DTM
The function `my_cast_dtm` casts our dataframes into a DTM.
```{r my_cast_dtm, eval = TRUE}
my_cast_dtm <- function(data) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

@@

rm(my_cast_dtm)
```
###Controls
The control parameters we use are:
```{r controls, eval = TRUE}
my_control <- list(

  nstart = 10,
  seed   = 1 : 10,
  best   = TRUE,

  burnin = 1000,
  iter   = 15000,
  thin   = 100

)
```
The control parameters we use for fast testing are:
```{r fast control}
my_control_fast <- list(

  nstart = 1,
  seed   = 1,
  best   = TRUE,

  burnin = 5,
  iter   = 10,
  thin   = 2

)
```

##Ideal Number of Topics Package Test
To decide the number of topics to discover, we run three different tests.
###Function
The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 
```{r function my_FindTopicsNumber }
my_FindTopicsNumber <- function(data_cast, n_topics){

  FindTopicsNumber(

  dtm = data_cast,
  topics = n_topics,
  metrics = c("CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  control = my_control,
  mc.cores = 4L

  )

}
```
###Train
```{r package test on topics, cache = TRUE}
#Start timer
start.time <- Sys.time()

#
##apply my_FindTopicsNumber
result_topic_test <- as_tibble(map(.x = d_cast, .f = my_FindTopicsNumber, n_topics = seq(from = 5, to = 100, by = 2)))

#Stop timer
end.time <- Sys.time()
print(end.time - start.time)

#
##Save results
#save(result_topic_test,
#     file = "Output/LDA_ntopics.RDATA") #this file still contains old results.
```
Previous separate experiments (from 20, to 40, by 5 topics) had the following time:
* Overview:     22min 
* Description:  11min 
* Manuals:      5.5hrs

###Graph 
We examine the result of the experiment by plotting them on a graph.
```{r LDA number topics plot}
#load("Output/LDA_ntopics.RDATA")

result_topic_test %>% map(.f = ldatuning::FindTopicsNumber_plot) #order is: Overview, Manuals, Description
```
From the results we see that the ideal number of topics is somewhere between 35 and 40.

## Fitting Model
The function `my_LDA` fits an LDA model on the DTM using the previous controls.
```{r my_LDA, eval= TRUE}
my_LDA <- function(n_topics, corpus, control = my_control){

  LDA_model <- LDA(
    x       = corpus,
    k       = n_topics,
    method  = "Gibbs",
    control = control
    )
}

###Functions for models (extract_dtm, get_distributions, perplexity)
The following functions are used as input in a map to compute and evaluate topic models. 
```{r getting gamma and beta, eval = TRUE}
#extract dtm
extract_dtm <- function(origin) d_cast[[origin]]

#extract Distributions (Gamma/Beta)
get_distributions <- function(model, distrib_str){ #input gamma or beta
  tidy(model, matrix = distrib_str)        %>%
    mutate(topic = paste("Topic", topic) ) %>%
      arrange(topic, desc(!!sym(distrib_str)))
}

#perplexity Function
my_perplexity <- function(model, dtm){
  perplexity(model, dtm, estimate_theta = FALSE)
}

The following functions allow us to inspect the results from our models(inspect distributions and get kw):
```{r}
 # get_top_match <- function(d_distribution){
 # 
 #  #save user input as string
 #  name_selected <- deparse(substitute(d_distribution)) #takes Gamma or Beta
 #  beta_gamma_sym <- tolower(name_selected)             #transforms to "gamma" or "beta"
 # 
 #  #Compute Case (Beta or Gamma, respectively)
 #  grouping         <- ifelse( name_selected == "Beta",  "topic", "document")
 #  objects_to_group <- ifelse( name_selected == "Beta",  "term",  "topic"   )
 #  top_num          <- ifelse( name_selected == "Beta",   10,      5       ) #select how many terms or topics(respectively) to show
 # 
 #  #
 #  ## DATA
 #  data.frame(d_distribution) %>%
 #    group_by(!!sym(grouping)) %>%
 #    top_n(top_num, !!sym(beta_gamma_sym)) %>%
 #    select(!!sym(grouping), !!sym(objects_to_group)) %>%
 #    group_by(!!sym(grouping)) %>%
 #    summarise(top = list(!!sym(objects_to_group)))
 # }

get_top_terms_topic <- function(d_beta){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    select(topic, term) %>%
    group_by(topic) %>%
    summarise(top_words = list(term))

@@

get_kw <- function(d_beta){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(3, beta) %>%
    ungroup()%>%
    pull(term)%>%
    unique()
}

```
###Training Models
We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`, along with the DTM used to build the model, the corpus of origin (overview or manuals), the word and topic distributions results from that model, it's evaluation measures, and vectors of words and topics that allow us humans to get a feel of the model, along with some key words.
```{r LDA fit, cache = TRUE, eval = TRUE}

test_topic_model <- tibble( #CHANGE NAME TO: topic_model

  #repeat each topic number twice (once for overview and once for manual)
  n_topic = rep(seq(from = 2, to = 4, by = 1), each = 2) # from = 5, to = 250, by = 5

  ) %>%
  mutate(Origin     = rep(c("overview", "manuals"), 3),         # should be 50
         `Topic ID` = paste(Origin, n_topic, sep = "_"),

         #Document Term Matrix
         DTM        = pmap(.l = list(Origin), .f = extract_dtm),

         #Fit Model
         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control_fast), #my_control

         #Gamma distribution
         Gamma = pmap(.l = list(Model), .f = get_distributions, distrib_str = "gamma"),

         #Beta distribution
         Beta = pmap(.l = list(Model),  .f = get_distributions, distrib_str = "beta"),

         #Perplexity
         Perplexity = pmap_dbl(.l = list(Model, DTM), .f = my_perplexity),

         #Loglikelihood
         LogLikelihood = pmap_dbl(.l = list(Model), .f = logLik), #this removes the degrees of freedom data

         #
         ##Inspect

@@

         #Select keywords
         kw = map(Beta, .f = get_kw)
         )

# Clean workspace

# rm(extract_dtm, get_distributions, my_perplexity,
#    get_top_terms_topic, get_top_topics_course, get_kw)

# test_topic_model
```

##Plots - Model Evaluation
To evaluate how many topics are optiomal, we graph the perplexity and log Likelihood of models against the number of topics.
```{r perplexity plots, eval = TRUE}
#Function
plot_evaluation <- function(origin){

  #data
  test_topic_model %>%

    #Wrangling
    select(n_topic, Origin, Perplexity, LogLikelihood) %>%
    gather(key = "Eval Type", value = "Eval Value", c(Perplexity, LogLikelihood)) %>%
    filter(Origin == origin) %>%

    #Graphics
    ggplot(mapping = aes(x = n_topic, y = `Eval Value`)) +
    geom_point() +
    geom_line() +
    facet_grid(rows = vars(`Eval Type`), scales = "free") +
    theme_minimal()

#Plot
plot_evaluation("overview")
plot_evaluation("manuals")
```

##Saving model_data:
We save our tibble with all the information.
```{r}
# save(topic_model, file = "Output/topic_model.RDATA" ) #needs to be renamed to match what is currently test_topic_model
```

#App
For our recommender system, we pass the distributions, number of topics, origin, and key words to the app.
##Distributions and Key words
The function `clean_kw` removes stopwords from our key words.
```{r function clean key words}
clean_kw <- function(kw_list){

  #stopwords
  kw_stopwords <- c("source", "primary", "type", "assess", "involve", "e.g", "discussion", "institute", "ha", "introduce",
                 "role","address", "student", "examination","coordinator", "maastrichtuniversity.nl", "identify", "manner", "mechanism", "concept", "hour",
                 "teach",  "depth","question", "specific", "busy","academic", "semester", "week", "test", "session", "team", "communicate", "theory", "text",
                 "library", "article", "examine", "current", "routledge", "temporary", "flow", "level", "study", "task")

  #remove stopwords
  kw <- setdiff(kw_list, kw_stopwords)
  #return
  return(kw[!is.na(kw)])

```
On our `topic_model` tibble we filter only information relevant for the app, and apply `clean_kw` on our `kw` column
```{r crop and clean TM for App}
app_topic_model <- test_topic_model %>% select(`Topic ID`, n_topic, Origin, Gamma, Beta, kw) %>%
  mutate(kw = map(kw, .f = clean_kw))
```

##Convenience Vectors
For the app we also need to have a list of all courses and an example of a prospective semester
```{r for convenience}
# set seed
set.seed(1)

#
## All courses
course_all <- d_course %>%
  inner_join(
    d_transcript,
    by = "Course ID"
  ) %>%
  distinct(
    `Course ID`
  ) %>%
  # remove semester abroad, skills and projects
  filter(
    ! str_detect(`Course ID`, pattern = "SA|SKI|PRO")
  ) %>%
  pull

#
##courses following_semester
course_following_semester <- sample(
  x       = course_all,
  size    = 60,
  replace = FALSE
  ) %>% sort

@@

```{r adding convenience vectors}
app_topic_model <- app_topic_model %>%
  mutate(`All Courses`     = course_all,
         `Sample semester` = course_following_semester)

#rm(course_all, course_following_semester)
```
## Saving files for APP
```{r app files}
# save(app_topic_model, file = "App/Recommender System/data_topic_models.RDATA")
```
# Visualization
### Functions 
This part is adapted 
```{r LDA prepare, eval = F}
prepare_data_LDA_beta <- function(d_beta){

  data.frame(d_beta) %>%
    mutate(topic = paste("Topic", topic)) %>%
      group_by(topic) %>%
        top_n(10, beta) %>%
      ungroup %>%
      arrange(topic, desc(beta))

} #repetition??? of inspect topics?

prepare_data_LDA_gamma <- function(d_gamma, level = Course){

  data_gamma <- data.frame(d_gamma) %>%
    mutate(topic = paste("Topic", topic)) %>%
    rename(`Course ID` = document)

  if(ensym(level) == sym("Course")) data_gamma <- data_gamma %>%
                                      rename(facet = `Course ID`)

  if(ensym(level) == sym("Cluster")) data_gamma <- data_gamma %>% 
                                       left_join(select(d_course, `Course ID`, Cluster), by = "Course ID") %>%
                                       filter(!is.na(Cluster)) %>%
                                       rename(facet = Cluster)

  if(ensym(level) == sym("Concentration")) data_gamma <- data_gamma %>%
                                             left_join(select(d_course, `Course ID`, Concentration, `Concentration (additional)`), by = "Course ID") %>%
                                             gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
                                             rename(facet = Concentration)

  data_gamma <- data_gamma %>%
    group_by(facet, topic) %>%
      summarise(gamma = sum(gamma)) %>%
    filter(gamma > 0.05) %>%
    ungroup %>%
    arrange(facet, desc(gamma))

  return(data_gamma)

# Bet Distribution
test <- list()

a <-  names(distribution)[1]
test[[a]] <- lapply(distribution[[a]],
                      prepare_data_LDA_beta)

# Gamma Distribution
b <- names(distribution)[2]
test[[b]] <- lapply(distribution[[b]],
                    prepare_data_LDA_gamma)

test <- test_topic_model %>%
  mutate(preparedBeta = pmap(list(Beta), .f = prepare_data_LDA_beta),
         preparededGamma = pmap(list(Gamma), .f = prepare_data_LDA_gamma)
         )
test[["preparedBeta"]]
rm(a,b #,test
   )
```
This part is not adapted
```{r LDA visualize, eval = F}
visualize_LDA_beta <- function(data_prepared, id_plot = "test"){

  data_prepared %>%
  ggplot(aes(x = reorder_within(term,
                                by = beta,
                                within = topic),
             y = beta,
             fill = topic)) +
    geom_col(show.legend = F) +
    facet_wrap(~ topic, scales = "free") +
    scale_x_reordered() +
    labs(x = "Terms", y = "Beta", title = "Main Terms of each Topic") +
    coord_flip() +
    theme_light() +
    theme(plot.title = element_text(hjust = 0.5))

  ggsave(paste(id_plot, "beta.jpeg"),
         width = 16, height = 10, path = "Plots/Topic Model")

visualize_LDA_gamma1 <- function(data_prepared, id_plot = "test"){

  data_prepared %>%
    ggplot(aes(reorder_within(facet, 
                              by = gamma, 
                              within = topic), 
               y = gamma, 
               fill = topic)) +
    geom_col(show.legend = F) +
    facet_wrap(~ topic, 
               scales = "free") +
    scale_x_reordered() +
    coord_flip() +
   # labs(x = ensym(facet), y = "Gamma", title = paste("Main", ensym(facet), "of each Topic") +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90, hjust = 0),
          plot.title = element_text(hjust = 0.5))

  ggsave(paste(id_plot, "gamma1.jpeg"),
         width = 16, height = 10, path = "Plots/Topic Model")

visualize_LDA_gamma2 <- function(data_prepared, id_plot = "test"){

  data_prepared %>%
    ggplot(aes(reorder_within(topic, 
                              by = gamma,
                              within = facet), 
               y = gamma, 
               fill = topic)) +
    geom_col(show.legend = F) +
    facet_wrap(~ facet, 
               scales = "free") +
    scale_x_reordered() +
    coord_flip() +
  #  labs(x = "Topics", y = "Gamma", title = "Main Topics of each Courses/Cluster") +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90, hjust = 0),
          plot.title = element_text(hjust = 0.5))

  ggsave(paste(id_plot, "gamma2.jpeg"),
         width = 16, height = 10, path = "Plots/Topic Model")

```{r LDA visualize all distrib, eval = F}
visualize_LDA_all_distrib <- function(data, level = Course, id_plot = "test"){

  # Beta distribution
  data %>% 
    prepare_data_LDA_beta %>%
    visualize_LDA_beta(id_plot = id_plot)

  # Gamma 1 distribution
  data %>% 
    prepare_data_LDA_gamma(level = !!ensym(level)) %>%
    visualize_LDA_gamma1(id_plot = id_plot)

  # Gamma 2 distribution
  data %>% 
    prepare_data_LDA_gamma(level = !!ensym(level)) %>%
    visualize_LDA_gamma2(id_plot = id_plot)

```{r LDA visualize all level, eval = F}
visualize_LDA_all_level <- function(data, id_plot = "test"){

  data %>% 
    visualize_LDA_all_distrib(level = Course,
                              id_plot = paste(id_plot, "_course"))

  data %>% 
    visualize_LDA_all_distrib(level = Cluster,
                              id_plot = paste(id_plot, "_cluster"))

  data %>% 
    visualize_LDA_all_distrib(level = Concentration,
                              id_plot = paste(id_plot, "_concentration"))

### Plots
```{r LDA plot, cache = TRUE, eval = F}
load("LDA.RDATA")

LDA_description_5 %>% visualize_LDA_all_level(id_plot = "description_k5")

LDA_overview_5 %>% visualize_LDA_all_level(id_plot = "overview_k5")

LDA_manual_5 %>% visualize_LDA_all_level(id_plot = "manual_k5")
```

```{r label, eval = FALSE, eval = F}
tidy(LDA_manual_10, "beta") %>%
  filter(beta > 1e-3) %>%
  bind_tf_idf(term = term, document = topic, n = beta) %>%
  group_by(topic) %>%
  top_n(10, tf_idf) %>%
  arrange(topic, desc(tf_idf))

  count(term, topic) %>%
  arrange(desc(n)) %>%

  filter(beta > 1e-3) %>%
  group_by(term) %>%
    mutate(n_topic = n(),
           beta = beta / n_topic) %>%
  group_by(topic) %>%
    top_n(10, beta)

  count(topic, term, wt = beta) %>%
  (term = term, document = topic, n = n) %>%
  group_by(topic) %>%
  top_n(10, tf_idf)

  group_by(term) %>%
  summarise(beta = sum(beta)) %>%
  arrange(desc(beta))

labels <- list(
  description_10 = "X"
)
```

```{r label bis, eval = FALSE}
visualize_LDA(LDA_cluster_10, id_plot = "Cluster, k = 10 with labelled topics", facet = T,
              topic_names = c("Psychology & Information", "Economics and Development", "Biology", "Chemistry and Math",
                              "Sociology", "Law", "Research", "International Politics",
                              "Philosophy", "Humanities"))

visualize_LDA(LDA_cluster_17, id_plot = "Cluster, k = 17 with labelled topics", facet = T,
              topic_names = c("Science/Knowledge", "Psycho", "Biology", "Chemistry", "Culture",
                              "Conflict", "Research", "Foreign Policy", "Arts", "Literature",
                              "Communication Skills", "Law", "Humanities", "Computer", "Economics", 
                              "Math", "Management and ?"))
visualize_LDA(LDA_cluster_25, id_plot = "Cluster, k = 25 with labelled topics", facet = T,
              topic_names = c(
                "Information", "Psycho", "Bio", "Chem", "Sociology",
                "History", "skills", "Europe", "Philosophy", "IR",
                "Conference", "Law", "Media", "Philosophy", "Economics",
                "Math", "Management and Literature", "Entrepreneurship", "Conflict", "Research",
                "Arts", "Computer Science", "Policy?", "Physiology", "Qual. Res."))
```

>>>>

---
title: "Pillar 2 - (STM) Topic Modeling"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
---

@@

#Topic Models
library(stm)
library(topicmodels)
library(quanteda) #used for DTM implementation called dfm

library(ggwordcloud) # Word Clouds

library(lemon)
library(ggthemes)
library(rlang) #quote
library(ldatuning) # ideal number of topics in LDA

@@

# STM
##Setup
###Cast DTM
The function `my_cast_dtm` casts our dataframes into a DTM (dfm from package quanteda)
```{r my_cast_dtm, eval = TRUE}
my_cast_dtm <- function(data) data %>%
  count(`Course ID`, word) %>%
  cast_dfm(`Course ID`, word, n)

@@

rm(my_cast_dtm)
```

###STM Corpus
We convert our DTMs into STM corpus to access to full functionality in STM package.
```{r as STM corpus, eval = TRUE}
stm_corpus <- d_cast %>% map(asSTMCorpus)
```

##Fitting STM
We will to train several models to have some flexibility in the number of topics we select. For this purpose we want to create two tibbles. One that trains on the entire data (for use), and one that we divide on training set and test set. 
###Functions
Several functions are needed to work with tibble and tidyverse functionality:
####My_stm Function
The function `my_LDA` fits an LDA model on the DTM using the previous controls.
```{r my_STM, eval= TRUE}
my_stm <- function(n_topics, corpus){

  STM_model <- stm(corpus$documents, corpus$vocab, K = n_topics, init.type = "Spectral")
}
```
####My_stm_eval Function
This function applied stm but with heldout vocab and documents. 
```{r}
my_stm_eval <- function(heldout, n_topic){
  stm::stm(heldout$documents, heldout$vocab, n_topic, init.type = "Spectral")
}
```

####Extraction Functions
We will be working with many lists of lists. The following functions help us extract information from lower levels of the list (e.g. access element in second list).
```{r getting gamma and beta, eval = TRUE}
#
##From external Lists:

#Extract DTM
extract_dtm <- function(origin) d_cast[[origin]]
#Extract CORPUS
extract_corpus <- function(origin) stm_corpus[[origin]]

#
## From STM_corpus class

#Extract documents
extract_documents <- function(corpus) corpus$documents
#Extract vocab
extract_vocab     <- function(corpus) corpus$vocab
#Extract data
extract_data     <- function(corpus) corpus$data

#
##From Partition

#Extract heldout docs
extract_held_doc <- function(heldout) heldout$documents#[[1]]
#Extract herlout vocab
extract_held_vocab <- function(heldout) heldout$vocab#[[1]]
#Extract missing
extract_helout_missing <- function(heldout) heldout$missing#[[1]]

#
## MODEL HELDOUT
my_model <- function(heldout){

  docs <- heldout$documents[[1]]
  voc  <- heldout$vocab
  k    <- n_topics

  Model <- stm(docs, voc, 5, init.type = "Spectral")

  return(Model)
}

#
##From Model
#tidy gamma
my_tidy_gamma <- function(Gamma, DTM){
  tidy(Gamma, matrix = "gamma", document_names = rownames(DTM))}

#extract

#extract Distributions (Gamma/Beta)
get_distributions <- function(model, distrib_str){ #input gamma or beta
  tidy(model, matrix = distrib_str)        %>%
    mutate(topic = paste("Topic", topic) ) %>%
      arrange(topic, desc(!!sym(distrib_str)))}

```
####Inspection functions
The following functions allow us to inspect the results from our models(inspect distributions and get kw):
```{r}
get_top_terms_topic <- function(d_beta){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    select(topic, term) %>%
    group_by(topic) %>%
    summarise(top_words = list(term))

@@

get_kw <- function(d_beta){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(3, beta) %>%
    ungroup()%>%
    pull(term)%>%
    unique()
}
```
###Model Tibbles
####For use:
```{r models in tibble}
topic_numbers <- seq(from = 5, to = 10, by = 5) # seq(from = 5, to = 20, by = 5) #seq(from = 5, to = 150, by = 5)

stm_model <- tibble(
  #repeat each topic number twice (once for overview and once for manual)
  n_topic = rep(topic_numbers, each = 2) ) %>%

  mutate(
    #Identification information
    Origin     = rep(c("overview", "manuals"), length(topic_numbers)),         
    `Topic ID` = paste(Origin, n_topic, sep = "_"),

    #DTM
    DTM       = pmap(.l = list(Origin), .f = extract_dtm),
    doc_names = map(DTM, rownames),

    #STM Corpus
    Corpus           = pmap(.l = list(Origin), .f = extract_corpus), 
    #Documents- STM corpus
    Documents_stm     = pmap(.l=list(Corpus),    .f = extract_documents),
    #Vocab- STM corpus
    Vocab_stm         = pmap(.l=list(Corpus),    .f = extract_vocab),
    #Data- STM corpus
    Data_stm          = pmap(.l=list(Corpus),    .f = extract_data),

    #Fit Model 
    Model  = pmap(.l = list(n_topic, Corpus), .f = my_stm),

    #Evaluation
    Exclusivity        = map(Model, exclusivity),
    semantic_coherence = pmap(.l = list(Model,DTM), semanticCoherence, M = 10), #M = num. of top words per topic
    #Alretnative input to semantic_coherence = pmap(.l = list(Model, Documents_stm), semanticCoherence, M = 10),

    #
    ##Inspection

    #Beta distribution
    Beta = pmap(.l = list(Model),  .f = tidy),
    #Gamma distribution
    Gamma = pmap(.l = list(Model, DTM), .f = my_tidy_gamma), #fix this

@@

    #Select keywords
    kw = map(Beta, .f = get_kw)

    #END MUTATE PARENTHESIS
         )

@@

```{r} 
#testing 
test_model <- stm_eval_model[1, ]

my_stm_eval(list(test_model$documents, test_model$vocab, test_model$n_topic))

my_stm_eval(documents = test_model$documents, vocab = test_model$vocab, n_topic = test_model$n_topic)

test <- list(test_model$documents, test_model$vocab, test_model$n_topic)
test %>% my_stm_eval

test <- list(stm_eval_model$documents, stm_eval_model$vocab, stm_eval_model$n_topic)

test %>% my_stm_eval

test <- stm_eval_model %>% mutate(test = list(documents, vocab, n_topic) %>% pmap(list))

stm_eval_model %>% mutate(test = test %>% map(my_stm_eval))
test1<- test$test[[1]]

####For evaluation
```{r models in tibble}
topic_numbers <-  seq(from = 5, to = 10, by = 5) #seq(from = 5, to = 150, by = 5)

#
##STM EVALUATION TIBBLE
stm_eval_model <- tibble(

  #repeat each topic number twice (once for overview and once for manual)
  n_topic = rep(topic_numbers, each = 2)

  ) %>%
  mutate(
    #Identification information
    Origin     = rep(c("overview", "manuals"), length(topic_numbers)),         
    `Topic ID` = paste(Origin, n_topic, sep = "_"),

    #DTM
    DTM       = pmap(.l = list(Origin),  .f = extract_dtm),
    Heldout   = pmap(.l = list(DTM),     .f = make.heldout, proportion = 0.5),

    #Fitting Model
    Model     = pmap(.l = list(Heldout, n_topic), .f = my_stm_eval),

    #Evaluation measures
    Exclusivity        = map(Model, exclusivity),

    semantic_coherence = pmap(.l = list(Model, Heldout), 
                              function(model,  heldout) semanticCoherence(model, heldout$documents)),

    eval_heldout       = pmap(.l = list(Model, Heldout), 
                              function(model,  heldout) eval.heldout(model, heldout$missing)),

    residual           = pmap(.l = list(Model, Heldout), 
                              function(model,  heldout) checkResiduals(model, heldout$documents, tol = 1/100)),

    bound              = pmap_dbl(.l = list(Model), 
                                  function(model) max(model$convergence$bound)),

    lfact              = map_dbl(Model,       
                                 function(model) lfactorial(model$settings$dim$K)),

    lbound             = bound + lfact,
    iterations         = map_dbl(Model,       
                                 function(model) length(model$convergence$bound))
    ) 
```

##Finding Number of Topics
We want to estimate the number of topics that exist in the data, to select a model for them.

###Using search K
`stm::searchK` helps in the search.
The function `findK` is used to vectorise searchK so we can apply it to the different elements of our corpus list (overview, manuals, description) in one go.
```{r findK}
#findK function 
findK <- function(dtm, k_topics){
  searchK(dtm$documents, dtm$vocab, K = k_topics, init.type = "Spectral")
}
```

We train models for 74 different numbers of topics (14-200 by 2).
Time estimate: for seq(from = 50, to = 100, by = 10) #18 models trained took 4:31-3:09 = (1 hour and 22 min)
```{r finding K}
#select number of topics
k_topics = seq(from = 4, to = 150, by = 2)

#Run findK
findingK <- stm_corpus %>%
  map(findK, k_topics)
```
We inspect the findings:
```{r plot evaluation}
findK_plots <- map(findingK, plot) #see how to show.
```

```{r save findK}
#save files
save(findingK, file= "STM_estimate_k.RDATA")

#clean
rm(findK, k_topics)
```
###Manual selection
